---
title: "Data Products Project"
author: "Ronaldo Ramírez"
date: "5/20/2022"
output: html_document
---

##Creating Server

```{1}
library(shiny)
library(ggplot2)
library(dplyr)
library(rsconnect)
# Select columns to be used in the analysis
diam <- diamonds[,c(1:4,7)]
# Define server logic required to draw a plot
shinyServer(function(input, output) {
        output$distPlot <- renderPlot({
                # Select diamonds depending of user input
                diam <- filter(diamonds, grepl(input$cut, cut), grepl(input$col, color), grepl(input$clar, clarity))
                # build linear regression model
                fit <- lm( price~carat, diam)
                # predicts the price
                pred <- predict(fit, newdata = data.frame(carat = input$car,
                                                          cut = input$cut,
                                                          color = input$col,
                                                          clarity = input$clar))
                # Draw the plot using ggplot2
                plot <- ggplot(data=diam, aes(x=carat, y = price))+
                        geom_point(aes(color = cut), alpha = 0.3)+
                        geom_smooth(method = "lm")+
                        geom_vline(xintercept = input$car, color = "red")+
                        geom_hline(yintercept = pred, color = "green")
                plot
        })
        output$result <- renderText({
                # Renders the text for the prediction below the graph
                diam <- filter(diamonds, grepl(input$cut, cut), grepl(input$col, color), grepl(input$clar, clarity))
                fit <- lm( price~carat, diam)
                pred <- predict(fit, newdata = data.frame(carat = input$car,
                                                          cut = input$cut,
                                                          color = input$col,
                                                          clarity = input$clar))
                res <- paste(round(pred, digits = 1.5),"$" )
                res
        })

})
```

## Creating UI
```{2}
library(shiny)

# Define UI for application that draws a histogram
shinyUI(fluidPage(

        # Application title
        titlePanel("Price predictor for Diamonds"),

        # Sidebar with options selectors
        sidebarLayout(
                sidebarPanel(
                        helpText("This application is a predictor for the price of a diamond based on its characteristics."),
                        h3(helpText("Select:")),
                        numericInput("car", label = h4("Carats"), step = 0.01, value = 1.5),
                        selectInput("cut", label = h4("Cut"),
                                    choices = list("Unknown" = "*", "Fair" = "Fair", "Good" = "^Good",
                                                   "Very Good" = "Very Good", "Premium" = "Premium",
                                                   "Ideal" = "Ideal")),
                        selectInput("col", label = h4("Color"),
                                    choices = list("Unknown" = "*", "D" = "D", "E" = "E",
                                                   "F" = "F", "G" ="G",
                                                   "H" = "H", "I" = "I",
                                                   "J" = "J")),
                        selectInput("clar", label = h4("Clarity"),
                                    choices = list("Unknown" = "*", "I1" = "I1", "SI2" = "SI2",
                                                   "SI1" = "SI1", "VS2" = "VS2", "VS1" = "VS1",
                                                   "VVS2" = "VVS2", "VVS1" = "VVS1", "IF" = "IF" ))
                ),

                # Show a plot with diamonds and regression line
                mainPanel(
                        plotOutput("distPlot"),
                        h4("Predicted value of this diamond is:"),
                        h3(textOutput("result"))
                )
        )
))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Analysis Report

Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Diamonds Properties can be analysed using several Parameters.
- Carat,Price,sample size,color Depth are some of the common parameters.
- This Report enables to pick the right parameters for the best Diamond selection.


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://rramirez.shinyapps.io/PricePredictorForDiamonds/

## Data Used
The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```